A quantitative framework for investigating the reliability of network construction

### 2019-03-26 manuscript/CI_interactions_accepted.tex
added disclaimers

\vspace{-.4in}

@@

\begin{spacing}{2.0}

@@

\linenumbers
\clearpage

@@

  \begin{figure}[h!]
    \caption{Nested levels of uncertainty mean that an observed interaction matrix is unlikely to capture all of the interactions that truly occur. Some feasible interactions (black squares in True matrix) are less likely than others (grey squares; lighter grey is less likely) based on species traits. For example, lions are less likely to predate upon elephants than zebras. If our trait model is incomplete (e.g., if we neglect group hunting in lions), we might assume that elephants are too large to be lion prey and assign this interaction a probability of 0.\\
    \indent Interactions occur with different probabilities in any given sample. We show six example networks representing interactions observed over two days at three sites. Interactions which occur during fewer sampling days are less likely to be observed.\\
    \indent Not all interactions are equally detectable. For example, interactions involving cryptic species are less likely to be observed.\\
    \indent After combining these layers of uncertainty, some interactions which truly occur are very unlikely to be observed. The observed matrix (bottom) is a subsample of the true matrix where the probability of observing each interaction depends upon multiple layers of uncertainty. Note that some low-probability interactions (e.g., lion predation on zebra) are included while others (e.g., lion predation on elephants) are not. For an illustration of the way in which these levels of uncertainty combine in simulated data, and the effects of uncertainty on network structure, see \emph{Appendix S1}. Attributions for images are given in \emph{Appendix S1-A}.}
    \label{conceptual_fig}
    \begin{center}
    % \includegraphics*[height=.45\textheight]{figures/conceptual_fig.eps}
    % \includegraphics*[height=.5\textheight]{Figure_1.eps}
    \end{center}
    \end{figure}

  \begin{figure}[h!]
      \caption{Despite the high replication in our empirical dataset, most galler-natural enemy pairs were never observed co-occurring and those that co-occurred rarely interacted. \textbf{A)} Histogram of the number of pairs of species observed co-occurring at least once. 9794 galler-enemy pairs were never observed co-occurring (not shown).
      \textbf{B)} Histogram of the number of observed interactions between co-occurring species. Species which co-occurred but never interacted are included. 
      \textbf{C)} For each species pair, the number of observed interactions plotted against the number of observed co-occurrences. The red, dashed line indicates a 1:1 relationship.}
      \label{histograms}
      \begin{center}
      % \includegraphics*[height=.6\textheight]{figures/GP_histogram.eps}
      % \includegraphics*[height=.6\textheight]{Figure_2.eps}
      \end{center}
      \end{figure}

  \begin{figure}[h!]
    \caption{Posterior distributions for the interaction probability ($\lambda_{ij}$) for two species that have not been observed interacting ($k_{ij}=0$), based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017}. Posterior distributions (curves) and 95\% credible intervals (lines at top of panel) for $\lambda_{ij}$ narrow and approach zero as the number of observed co-occurrences ($n_{ij}$) increases. Diamonds indicate the maximum likelihood estimator for the mean probability of interaction.
    Dashed lines indicate threshold probabilities of 0.01, 0.05, and 0.1. The number of samples required to obtain a 95\% credible interval below each threshold increases rapidly. It takes just over 20 observed co-occurrences to be 95\% confident that $\lambda_{ij}<0.10$ but over 100 co-occurrences to be 95\% confident that $\lambda_{ij}<0.01$.}
    \label{Salix_pdfs_cdfs}
    \begin{center}
    % \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
    % \includegraphics*[width=.8\textwidth]{Figure_3.eps}
    \end{center}
    \end{figure}

  \begin{figure}[h!]
    \caption{Posterior distributions for the interaction probability ($\lambda_{ij}$) for two species that have not been observed interacting ($k_{ij}=0$), A) based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017} and B) based on a network describing interactions between gallers and several genotypes of \emph{Salix hookeriana} from~\citet{Barbour2016}. Posterior distributions (curves) and 95\% credible intervals (lines at top of panel) for $\lambda_{ij}$ narrow and approach zero as the number of observed co-occurrences ($n_{ij}$) increases. Diamonds indicate the maximum likelihood estimator for the mean probability of interaction.
    Dashed lines indicate threshold probabilities of 0.01, 0.05, and 0.1. Note that both priors constrain the MLE of $\lambda_{ij}$ above 0.1 and that the posterior probability distributions become similar for very high $n$.}
    \label{prior_comparison}
    \begin{center}
    % \includegraphics*[width=.8\textwidth]{figures/SG_pdfs_prior_comparison.eps}
    % \includegraphics*[width=.8\textwidth]{Figure_4.eps}
    \end{center}
    \end{figure}

>>>>

\vspace{-.2in}

This is the peer reviewed version of the following article:~\citet{Cirtwill2019}, which has been published in final form at \textbf{Methods in Ecology and Evolution} (DOI: 10.1111/2041-210X.13180). This article may be used for non-commercial purposes in accordance with Wiley Terms and Conditions for Use of Self-Archived Versions.

@@

\begin{spacing}{1.0}

@@

\end{spacing}{1.0}
\begin{spacing}{1.5}

% \linenumbers
\clearpage

@@

  \begin{figure}[h!]
    \caption{Nested levels of uncertainty mean that an observed interaction matrix is unlikely to capture all of the interactions that truly occur. Some feasible interactions (black squares in True matrix) are less likely than others (grey squares; lighter grey is less likely) based on species traits. For example, lions are less likely to predate upon elephants than zebras. If our trait model is incomplete (e.g., if we neglect group hunting in lions), we might assume that elephants are too large to be lion prey and assign this interaction a probability of 0.\\
    \indent Interactions occur with different probabilities in any given sample. We show six example networks representing interactions observed over two days at three sites. Interactions which occur during fewer sampling days are less likely to be observed.\\
    \indent Not all interactions are equally detectable. For example, interactions involving cryptic species are less likely to be observed.\\
    \indent After combining these layers of uncertainty, some interactions which truly occur are very unlikely to be observed. The observed matrix (bottom) is a subsample of the true matrix where the probability of observing each interaction depends upon multiple layers of uncertainty. Note that some low-probability interactions (e.g., lion predation on zebra) are included while others (e.g., lion predation on elephants) are not. For an illustration of the way in which these levels of uncertainty combine in simulated data, and the effects of uncertainty on network structure, see \emph{Appendix S1}. Attributions for images are given in \emph{Appendix S1-A}.}
    \label{conceptual_fig}
    \begin{center}
    % \includegraphics*[height=.45\textheight]{figures/conceptual_fig.eps}
    \includegraphics*[height=.5\textheight]{Figure_1.eps}
    \end{center}
    \end{figure}

  \begin{figure}[h!]
      \caption{Despite the high replication in our empirical dataset, most galler-natural enemy pairs were never observed co-occurring and those that co-occurred rarely interacted. \textbf{A)} Histogram of the number of pairs of species observed co-occurring at least once. 9794 galler-enemy pairs were never observed co-occurring (not shown).
      \textbf{B)} Histogram of the number of observed interactions between co-occurring species. Species which co-occurred but never interacted are included. 
      \textbf{C)} For each species pair, the number of observed interactions plotted against the number of observed co-occurrences. The red, dashed line indicates a 1:1 relationship.}
      \label{histograms}
      \begin{center}
      % \includegraphics*[height=.6\textheight]{figures/GP_histogram.eps}
      \includegraphics*[height=.6\textheight]{Figure_2.eps}
      \end{center}
      \end{figure}

  \begin{figure}[h!]
    \caption{Posterior distributions for the interaction probability ($\lambda_{ij}$) for two species that have not been observed interacting ($k_{ij}=0$), based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017}. Posterior distributions (curves) and 95\% credible intervals (lines at top of panel) for $\lambda_{ij}$ narrow and approach zero as the number of observed co-occurrences ($n_{ij}$) increases. Diamonds indicate the maximum likelihood estimator for the mean probability of interaction.
    Dashed lines indicate threshold probabilities of 0.01, 0.05, and 0.1. The number of samples required to obtain a 95\% credible interval below each threshold increases rapidly. It takes just over 20 observed co-occurrences to be 95\% confident that $\lambda_{ij}<0.10$ but over 100 co-occurrences to be 95\% confident that $\lambda_{ij}<0.01$.}
    \label{Salix_pdfs_cdfs}
    \begin{center}
    % \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
    \includegraphics*[width=.8\textwidth]{Figure_3.eps}
    \end{center}
    \end{figure}

  \begin{figure}[h!]
    \caption{Posterior distributions for the interaction probability ($\lambda_{ij}$) for two species that have not been observed interacting ($k_{ij}=0$), A) based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017} and B) based on a network describing interactions between gallers and several genotypes of \emph{Salix hookeriana} from~\citet{Barbour2016}. Posterior distributions (curves) and 95\% credible intervals (lines at top of panel) for $\lambda_{ij}$ narrow and approach zero as the number of observed co-occurrences ($n_{ij}$) increases. Diamonds indicate the maximum likelihood estimator for the mean probability of interaction.
    Dashed lines indicate threshold probabilities of 0.01, 0.05, and 0.1. Note that both priors constrain the MLE of $\lambda_{ij}$ above 0.1 and that the posterior probability distributions become similar for very high $n$.}
    \label{prior_comparison}
    \begin{center}
    % \includegraphics*[width=.8\textwidth]{figures/SG_pdfs_prior_comparison.eps}
    \includegraphics*[width=.8\textwidth]{Figure_4.eps}
    \end{center}
    \end{figure}

### 2019-03-26 manuscript/CI_preprint.tex
added disclaimers

\vspace{-.4in}

>>>>

\vspace{-.2in}

This is the pre-peer reviewed version. This article has been published in final form at \textbf{Methods in Ecology and Evolution} (DOI: 10.1111/2041-210X.13180). This article may be used for non-commercial purposes in accordance with Wiley Terms and Conditions for Use of Self-Archived Versions. Text of the peer-reviewed accepted version will be uploaded March 26, 2020.
